% !TXS template
\documentclass[10pt,a4paper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.85,a4paper]{geometry}
\usepackage{babel}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Braden}
\familyname{Bowdish}
\mobile{484 680 5549}
\email{bmbowdish@live.com}
\extrainfo{GitHub.com/bmbowdish}


\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Objective}
 \cvlistitem{Seeking a Software Engineering internship for Spring of 2019.}
\section{Education}
  \cvlistitem{Rochester Institute of Technology. Bachelors of Science, Computer Science. 2015-2018.}
  \subsection{Relevant Classes}
    \cvlistitem{Data Structures}
    \cvlistitem{Object Oriented Programming}
    \cvlistitem{Mechanics of Programming}
    \cvlistitem{Intro to Software Engineering}
\section{Experience}
  \cventry{--}{The Penn Mutual Life Insurance Company}{}{Worked as a DevOps intern on the Linux Team. This includes writing Python and Bash scripts, as well as provisioning many of the virtual machines that needed to be created.}{Fall 2018}{}
  \cventry{--}{TD Alfredo's Pizzeria}{}{Worked as a Cashier and Delivery Driver in a local Pizza shop}{2016-2018}{}
\section{Projects}
 \cventry{--}{Swiftfall}{\href{https://github.com/bmbowdish/Swiftfall}{(github.com/bmbowdish/Swiftfall)}}{Created an open-source wrapper for the Scryfall API. Swiftfall takes JSON data from the Scryfall API and turns the data into Objects that any developer can use in their iOS App}{Spring 2018}{} 
 \cventry{--}{Magic App}{\href{https://github.com/bmbowdish/BrickHack-Magic-App}{(github.com/bmbowdish/BrickHack-Magic-App)}}{Developed an iOS and Apple Watch app which generates random numbers and tracks life totals for the Magic the Gathering card game. First Swift project, completed at BrickHack 4} {Spring 2018}{}
  \cventry{--}{Event Keeper}{\href{https://github.com/bmbowdish/Event-Keeper}{(github.com/bmbowdish/Event-Keeper)}}{Created a Python application which controls an Arduino that reads iButtons and is run on a Raspberry Pi. Event Keeper can take attendance during Computer Science House meetings} {Fall 2015}{}
 \cventry{--}{LED Matrix}{\href{https://github.com/bmbowdish/LED-Hackathon-Matrix}{(github.com/bmbowdish/LED-Hackathon-Matrix)}}{LED Matrix which is controlled by a simple joypad. Joypad allows user to pick which lights turn on in which order}{Spring 2017}{}
  \cventry{--}{Web Checkers}{}{Online Checkers game built in java using the Spark framework. Working with four other developers for 15 weeks. Implemented the Checkerboard and Kinging of Pieces, as well as leading Source Control}{Spring 2017}{}
\section{Technical Skills}
  \cvitemwithcomment{}{Swift, Python, Git, Github, Bash, Java, C, \LaTeX}{}
\section{Extracurriculars}
  \cvitem{--}{Computer Science House: A living-learning community for people interested in computers and other forms of technology.}
  \cvitem{--}{CSH History Director: Leading a committee devoted to alumni outreach and event planning.}
\end{document}
